---
title: "Project"
author: "Dipankar Lahiri"
date: "2025-04-25"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr)
library(forcats)
library(stringr)
library(ggplot2)
library(rstatix)
library(ggdist)
library(gt)
library(tidyverse)

my_df <- read_csv("/Users/dipankarlahiri/Desktop/Project/AI Responses Combined.csv")
colnames(my_df)[4] <- "AI Use"
colnames(my_df)[5] <- "AI Purpose"
colnames(my_df)[6] <- "Replace Human"
colnames(my_df)[7] <- "Productive"
colnames(my_df)[9] <- "Grade"
colnames(my_df)[10] <- "Income"
colnames(my_df)[13] <- "Social media use"
colnames(my_df)[14] <- "Subject"
my_df$Gender <- ifelse(str_to_lower(my_df$Gender) == "female", "Female", "Not Female")
ai_use_order <- c("Never", "Less than 5 minutes", "Between 5 minutes and 30 minutes", 
                  "30 minutes to 2 hours", "More than 2 hours")
my_df$`AI Use` <- factor(my_df$`AI Use`, levels = ai_use_order, ordered = TRUE)
my_df$`AI Purpose` <- ifelse(
  str_detect(my_df$`AI Purpose`, "Learning \\(e\\.g\\., studying, academic help\\)|Work \\(e\\.g\\., professional tasks, projects\\)"),
  "Learning/Work", "Others"
)
my_df$`Replace Human` <- ifelse(str_to_lower(my_df$`Replace Human`) == "no", "No", "Yes")
my_df$Productive <- ifelse(str_to_lower(my_df$Productive) == "yes", "Yes", "No")
my_df$Grade <- ifelse(my_df$Grade %in% c("Excellent (Top grades in most subjects)", "Good (Above-average performance)"),
                      "Good", "Bad")
my_df$Income <- ifelse(my_df$Income %in% c("High (Significantly above the national average)",
                                           "Upper-Middle (Above the national average)"),
                       "High", "Low")
my_df <- my_df %>%
  mutate(`Social Skills` = `Social confidence` - `Social awkwardness`) %>%
  select(-`Social confidence`, -`Social awkwardness`)
social_media_order <- c("Less than 1 hour", "Between 1 and 2 hours", 
                        "Between 3 and 4 hours", "Between 4 and 5 hours", "More than 5 hours")
my_df$`Social media use` <- factor(my_df$`Social media use`, levels = social_media_order, ordered = TRUE)
my_df$Subject <- ifelse(my_df$Subject %in% c("Social Sciences", "Humanities"), "Arts", "Science")
my_df <- my_df %>% select(-13)
my_df$`AI Use` <- recode(my_df$`AI Use`,
  "Never" = 0,
  "Less than 5 minutes" = 1,
  "Between 5 minutes and 30 minutes" = 2,
  "30 minutes to 2 hours" = 3,
  "More than 2 hours" = 4
)
my_df$`Social media use` <- recode(my_df$`Social media use`,
  "Less than 1 hour" = 1,
  "Between 1 and 2 hours" = 2,
  "Between 3 and 4 hours" = 3,
  "Between 4 and 5 hours" = 4,
  "More than 5 hours" = 5
)

my_df <- my_df %>% select(Gender, Subject, `AI Use`, Trust, Age, Nationality, `Replace Human`, Productive)
```

# Descriptive Stats, Viz.

## Age

```{r}
summary(my_df$Age)
hist(my_df$Age, main = "Age Distribution", xlab = "Age", col = "skyblue", breaks = 10)
```

## Gender

```{r}
table(my_df$Gender)
barplot(table(my_df$Gender), main = "Gender Distribution", col = "lightgreen", ylab = "Count")


```

## AI Use

```{r}
summary(my_df$`AI Use`)
ai_use_summary <- my_df %>%
  count(`AI Use`) %>%
  mutate(Percentage = n / sum(n) * 100) %>%
  rename(Count = n, `AI Use Level` = `AI Use`)
print(ai_use_summary)
hist(my_df$`AI Use`, main = "AI Use (increasing intensity)", xlab = "AI Use Score", col = "lightblue", breaks = 5)

```


## Used AI to replace human?

```{r}
table(my_df$`Replace Human`)
barplot(table(my_df$`Replace Human`), main = "Ever Replaced Human?", col = "orchid", ylab = "Count")


```

# Productivity with AI

```{r}
table(my_df$Productive)
barplot(table(my_df$Productive), main = "Feels More Productive with AI?", col = "gold", ylab = "Count")

```

## AI Trust

```{r}
summary(my_df$Trust)
trust_summary <- my_df %>%
  count(`Trust`) %>%
  mutate(Percentage = n / sum(n) * 100) %>%
  rename(Count = n, `Trust Level` = `Trust`)
print(trust_summary)
hist(my_df$Trust, main = "Trust in AI", xlab = "Trust Score", col = "skyblue", breaks = 5)

```

## Subject

```{r}
table(my_df$Subject)
barplot(table(my_df$Subject), main = "Field of Study", col = "steelblue", ylab = "Count")


```

# Correlation tests (N=155)

## H1: Males use AI chatbots more than females.

```{r}

### 1. DESCRIPTIVE STATISTICS ###
h1_table <- my_df %>%
  group_by(Gender) %>%
  summarise(
    n = n(),
    Median = median(`AI Use`),
    Mean = round(mean(`AI Use`), 2),
    SD = round(sd(`AI Use`), 2),
    Min = min(`AI Use`),
    Max = max(`AI Use`),
    .groups = 'drop'
  ) %>%
  gt() %>%
  tab_header(
    title = md("**AI Chatbot Usage by Gender**"),
    subtitle = "0-4 scale (Higher = more frequent use)"
  ) %>%
  fmt_number(columns = c(Mean, SD), decimals = 2) %>%
  cols_label(
    n = md("**N**"),
    Median = md("**Median**"),
    Mean = md("**Mean**"),
    SD = md("**SD**")
  )

### 2. VISUALIZATIONS ###
# Heatmap
heatmap_plot <- my_df %>%
  count(Gender, `AI Use`) %>%
  ggplot(aes(Gender, `AI Use`, fill = n)) +
  geom_tile(color = "white") +
  geom_text(aes(label = n), color = "white") +
  scale_fill_gradient(low = "#4ECDC4", high = "#FF6B6B") +
  labs(title = "AI Use Frequency Distribution by Gender")

# Boxplot
boxplot <- ggplot(my_df, aes(Gender, `AI Use`, fill = Gender)) +
  geom_boxplot() +
  scale_fill_manual(values = c("Not Female" = "#4ECDC4", "Female" = "#FF6B6B")) +
  labs(title = "Distribution of AI Use Frequency")

### 3. ORDINAL ANALYSIS ###
wilcox_result <- wilcox.test(`AI Use` ~ Gender, data = my_df, exact = FALSE)
effsize <- wilcox_effsize(`AI Use` ~ Gender, data = my_df, ci = TRUE)

### 4. BINARY ANALYSIS ###
my_df <- my_df %>%
  mutate(AI_Use_Binary = factor(ifelse(`AI Use` >= 3, "High", "Low"), 
                               levels = c("Low", "High")))

# Enhanced Contingency Table with Odds Calculation
contingency_table <- my_df %>%
  group_by(Gender, AI_Use_Binary) %>%
  summarise(Count = n(), .groups = "drop") %>%
  pivot_wider(names_from = AI_Use_Binary, values_from = Count) %>%
  mutate(
    Total = Low + High,
    `% High` = round(High/Total*100, 1),
    `Within-Group Odds (High/Low)` = round(High / Low, 2)
  ) %>%
  gt() %>%
  tab_header(title = "High vs Low AI Use by Gender") %>%
  fmt_number(columns = c(Low, High, Total, `Within-Group Odds (High/Low)`), decimals = 2) %>%
  cols_label(
    `% High` = md("**% High**"),
    `Within-Group Odds (High/Low)` = md("**Within-Group Odds (High/Low)**")
  )

# Correct Odds Ratio Calculation
tab <- table(my_df$Gender, my_df$AI_Use_Binary)

a <- 17
b <- 16
c <- 21
d <- 101

or <- (a * d) / (b * c)
or_se <- sqrt(1/a + 1/b + 1/c + 1/d)
or_ci <- exp(log(or) + c(-1.96, 1.96) * or_se)

# Chi-square Test
chi_test <- chisq.test(tab)

### 5. FINAL REPORTING ###
cat("\n--- H1: Males use AI chatbots more than females ---\n\n")

male_median <- h1_table$`_data`$Median[h1_table$`_data`$Gender == "Not Female"]
female_median <- h1_table$`_data`$Median[h1_table$`_data`$Gender == "Female"]

cat("Ordinal Analysis:\n")
cat(sprintf(
  "Males reported significantly higher AI use frequencies (Mdn = %.1f vs. Females Mdn = %.1f; Mann-Whitney U = %.0f, *p* = %.3f).\n",
  male_median, female_median,
  wilcox_result$statistic,
  wilcox_result$p.value
))
cat(sprintf(
  "The effect size was small-to-medium (rank-biserial *r* = %.2f, 95%% CI [%.2f, %.2f]), indicating a %.1f%% probability that a randomly selected male would report higher usage than a female (95%% CI [%.1f%%, %.1f%%]).\n\n",
  effsize$effsize,
  effsize$conf.low,
  effsize$conf.high,
  (effsize$effsize + 1)/2 * 100,
  (effsize$conf.low + 1)/2 * 100,
  (effsize$conf.high + 1)/2 * 100
))

cat("Binary Analysis:\n")
cat(sprintf(
  "Males had %.1f× higher odds of being high-frequency users (≥3 on the scale) (χ²(1) = %.2f, *p* = %.3f; 95%% CI [%.2f, %.2f]).\n",
  or,
  chi_test$statistic,
  chi_test$p.value,
  or_ci[1],
  or_ci[2]
))

# Display all outputs
h1_table
contingency_table
heatmap_plot
boxplot

```

Justification: Medians, resisting outliers, clearly show males cluster at "3" (AI use) vs. females at "2" (AI use).
An ordinal outcome (AI Use on a Likert-type scale) and independent groups (gender) necessitated a non-parametric approach. The Wilcoxon rank-sum test (Mann-Whitney U) was chosen to detect differences in AI use frequency without assuming normality. Effect size (rank-biserial r) and probability of superiority were reported to convey practical significance beyond p-values.
To complement the ordinal analysis, a binary categorisation (low vs. high AI use) was created to facilitate a chi-square test of independence. This allowed for the examination of proportional differences in high-frequency usage between genders. The odds ratio and its confidence interval were calculated to quantify the strength and direction of the association. 95% confident that the true odds ratio is somewhere between 2.23 and 11.71. Why Chi-square (not Fisher’s)? All expected counts >5 (no small-cell bias).
Both tests agree (medians and ORs show male > female use).Narrow CIs (e.g., OR CI [2.23, 11.71] excludes 1 = strong evidence).

## H2: Males show higher levels of trust for information generated by AI chatbots than females.

```{r}

### PREP: Make Trust numeric early ###
my_df <- my_df %>%
  mutate(Trust = as.numeric(as.character(Trust)))

### 1. DESCRIPTIVE STATISTICS ###
h2_table <- my_df %>%
  group_by(Gender) %>%
  summarise(
    n = n(),
    Median = median(Trust),
    Mean = round(mean(Trust), 2),
    SD = round(sd(Trust), 2),
    Min = min(Trust),
    Max = max(Trust),
    .groups = 'drop'
  ) %>%
  gt() %>%
  tab_header(
    title = md("**AI Trust Levels by Gender**"),
    subtitle = "1-5 scale (Higher = more trust)"
  ) %>%
  fmt_number(columns = c(Mean, SD), decimals = 2) %>%
  cols_label(
    n = md("**N**"),
    Median = md("**Median**"),
    Mean = md("**Mean**"),
    SD = md("**SD**")
  )

### 2. VISUALIZATIONS ###
# For plotting only: Treat Trust as factor, temporary
my_df_plot <- my_df %>%
  mutate(Trust = factor(Trust, levels = sort(unique(Trust), decreasing = TRUE)))

# Stacked bar chart
ggplot(my_df_plot, aes(Gender, fill = Trust)) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "RdYlGn", direction = -1) +
  scale_y_continuous(labels = scales::percent) +  # <-- add this
  labs(title = "AI Trust Distribution by Gender", y = "Percentage")

# Jitter plot with medians
trust_summary_gender <- my_df %>%
  group_by(Gender) %>%
  summarise(median = median(Trust), .groups = "drop")

ggplot(my_df, aes(Gender, Trust, color = Gender)) +
  geom_jitter(width = 0.15, alpha = 0.4) +
  geom_point(
    data = trust_summary_gender, 
    aes(y = median), 
    shape = 21, size = 8, fill = "white"
  ) +
  geom_text(
    data = trust_summary_gender,
    aes(y = median, label = median), 
    color = "black", size = 3.5
  ) +
  scale_color_manual(values = c("Not Female" = "#4ECDC4", "Female" = "#FF6B6B")) +
  labs(title = "Gender Differences in AI Trust")

### 3. ORDINAL ANALYSIS ###
wilcox_result <- wilcox.test(Trust ~ Gender, data = my_df, exact = FALSE)
effsize <- wilcox_effsize(Trust ~ Gender, data = my_df, ci = TRUE)

### 4. BINARY ANALYSIS ###
# Dichotomize Trust (High = 4-5, Low = 1-3)
my_df <- my_df %>% 
  mutate(High_Trust = ifelse(Trust >= 4, "High", "Low"))

contingency_table <- my_df %>%
  group_by(Gender, High_Trust) %>%
  summarise(Count = n(), .groups = "drop") %>%
  pivot_wider(names_from = High_Trust, values_from = Count) %>%
  mutate(
    Total = Low + High,
    `% High` = round(High / Total * 100, 1),
    `Within-Group Odds (High/Low)` = round(High / Low, 2)
  ) %>%
  gt() %>%
  tab_header(title = "High vs Low AI Trust by Gender") %>%
  fmt_number(columns = c(Low, High, Total, `Within-Group Odds (High/Low)`), decimals = 2) %>%
  cols_label(
    `% High` = md("**% High**"),
    `Within-Group Odds (High/Low)` = md("**Within-Group Odds (High/Low)**")
  )

# Odds Ratio Calculation
a <- 18
b <- 15
c <- 35
d <- 87
or <- (a * d) / (b * c)
or_ci <- exp(log(or) + c(-1.96, 1.96) * sqrt(1/a + 1/b + 1/c + 1/d))

# Chi-square Test
cont_table <- matrix(c(a, b, c, d), nrow = 2)
chi_test <- chisq.test(cont_table)

### 5. REPORTING ###
cat("--- H2: Males show higher trust in AI-generated information ---\n\n")

cat("Ordinal Analysis:\n")
cat(sprintf(
  "Males reported higher trust levels (Mdn = %.1f vs. Females Mdn = %.1f; Mann-Whitney U = %.0f, p = %.3f).\n",
  h2_table$Median[h2_table$Gender == "Not Female"],
  h2_table$Median[h2_table$Gender == "Female"],
  wilcox_result$statistic,
  wilcox_result$p.value
))
cat(sprintf(
  "Effect size: r = %.2f (95%% CI [%.2f, %.2f]). Probability superiority = %.1f%% (95%% CI [%.1f%%, %.1f%%]).\n\n",
  effsize$effsize,
  effsize$conf.low,
  effsize$conf.high,
  (effsize$effsize + 1)/2 * 100,
  (effsize$conf.low + 1)/2 * 100,
  (effsize$conf.high + 1)/2 * 100
))

cat("Binary Analysis (Trust ≥4):\n")
cat(sprintf(
  "Males had %.1f× higher odds of high trust (χ²(1) = %.2f, p = %.3f; 95%% CI [%.2f, %.2f]).",
  or,
  chi_test$statistic,
  chi_test$p.value,
  or_ci[1],
  or_ci[2]
))

# Display tables
h2_table
contingency_table


```

A Wilcoxon rank-sum test revealed that males reported significantly higher trust in AI-generated information (Mdn = 4.0) compared to females (Mdn = 3.0), U = 1484, p = .011. The effect size was small-to-moderate, r = .21, 95% CI [.03, .37], with a probability of superiority of 60.3% (95% CI [51.5%, 68.5%]).
To complement the ordinal analysis, trust was dichotomized, and a chi-square test showed a significant association between gender and high trust rates, χ²(1) = 6.61, p = .010. Males had 3.0 times greater odds of reporting high trust compared to females, 95% CI [1.35, 6.57].

## H3: Those who study STEM subjects show higher levels of trust for information generated by AI chatbots than those who study Humanities and Social Sciences.

```{r}

### 1. DESCRIPTIVE STATISTICS ###
h3_table <- my_df %>%
  group_by(Subject) %>%
  summarise(
    n = n(),
    Median = median(Trust),
    Mean = round(mean(Trust), 2),
    SD = round(sd(Trust), 2),
    Min = min(Trust),
    Max = max(Trust),
    .groups = 'drop'
  ) %>%
  gt() %>%
  tab_header(
    title = md("**AI Trust Levels by Field of Study**"),
    subtitle = "STEM vs Humanities/Social Sciences"
  ) %>%
  fmt_number(columns = c(Mean, SD), decimals = 2) %>%
  cols_label(
    n = md("**N**"),
    Median = md("**Median**"),
    Mean = md("**Mean**"),
    SD = md("**SD**")
  )

### 2. VISUALIZATIONS ###
# Stacked bar chart
my_df_plot_h3 <- my_df %>%
  mutate(Trust = factor(Trust, levels = sort(unique(Trust), decreasing = TRUE)))

# Stacked bar chart (fixed)
ggplot(my_df_plot_h3, aes(Subject, fill = Trust)) +
  geom_bar(position = "fill") +
  scale_fill_brewer(palette = "RdYlGn", direction = -1) +
  scale_y_continuous(labels = scales::percent) +
  labs(
    title = "AI Trust Distribution by Field of Study",
    y = "Percentage"
  )

# Jitter plot with medians
trust_summary <- my_df %>%
  group_by(Subject) %>%
  summarise(median = median(Trust))

ggplot(my_df, aes(Subject, Trust, color = Subject)) +
  geom_jitter(width = 0.15, alpha = 0.4) +
  geom_point(
    data = trust_summary,
    aes(y = median),
    shape = 21, size = 8, fill = "white"
  ) +
  geom_text(
    data = trust_summary,
    aes(y = median, label = median),
    color = "black", size = 3.5
  ) +
  scale_color_manual(values = c("Science" = "#4ECDC4", "Arts" = "#FF6B6B")) +
  labs(title = "Field of Study Differences in AI Trust")

### 3. ORDINAL ANALYSIS ###
wilcox_result <- wilcox.test(Trust ~ Subject, data = my_df, exact = FALSE)
effsize <- wilcox_effsize(Trust ~ Subject, data = my_df, ci = TRUE)

### 4. BINARY ANALYSIS ###
# Dichotomize Trust (High = 4-5, Low = 1-3)
my_df <- my_df %>%
  mutate(High_Trust = ifelse(Trust >= 4, "High", "Low"))

contingency_table_h3 <- my_df %>%
  group_by(Subject, High_Trust) %>%
  summarise(Count = n(), .groups = "drop") %>%
  pivot_wider(names_from = High_Trust, values_from = Count) %>%
  mutate(
    Total = Low + High,
    `% High` = round(High / Total * 100, 1),
    `Within-Group Odds (High/Low)` = round(High / Low, 2)
  ) %>%
  gt() %>%
  tab_header(title = "High vs Low AI Trust by Field of Study") %>%
  fmt_number(columns = c(Low, High, Total, `Within-Group Odds (High/Low)`), decimals = 2) %>%
  cols_label(
    `% High` = md("**% High**"),
    `Within-Group Odds (High/Low)` = md("**Within-Group Odds (High/Low)**")
  )

# Odds Ratio Calculation
# (Adjust 'a', 'b', 'c', 'd' from your actual output!)
cont_table <- table(my_df$Subject, my_df$High_Trust)
a <- cont_table["Science", "High"]
b <- cont_table["Science", "Low"]
c <- cont_table["Arts", "High"]
d <- cont_table["Arts", "Low"]

or <- (a * d) / (b * c)
or_ci <- exp(log(or) + c(-1.96, 1.96) * sqrt(1/a + 1/b + 1/c + 1/d))

# Chi-square Test
chi_test <- chisq.test(cont_table)

### 5. REPORTING ###
cat("--- H3: STEM students show higher trust in AI-generated information ---\n\n")

cat("Ordinal Analysis:\n")
cat(sprintf(
  "STEM students reported higher trust levels (Mdn = %.1f vs. Humanities/Social Sciences Mdn = %.1f; Mann-Whitney U = %.0f, p = %.3f).\n",
  h3_table$`_data`$Median[h3_table$`_data`$Subject == "Science"],
  h3_table$`_data`$Median[h3_table$`_data`$Subject == "Arts"],
  wilcox_result$statistic,
  wilcox_result$p.value
))
cat(sprintf(
  "Effect size: r = %.2f (95%% CI [%.2f, %.2f]). Probability superiority = %.1f%% (95%% CI [%.1f%%, %.1f%%]).\n\n",
  effsize$effsize,
  effsize$conf.low,
  effsize$conf.high,
  (effsize$effsize + 1)/2 * 100,
  (effsize$conf.low + 1)/2 * 100,
  (effsize$conf.high + 1)/2 * 100
))

cat("Binary Analysis (Trust ≥4):\n")
cat(sprintf(
  "STEM students had %.1f× higher odds of high trust (χ²(1) = %.2f, p = %.3f; 95%% CI [%.2f, %.2f]).",
  or,
  chi_test$statistic,
  chi_test$p.value,
  or_ci[1],
  or_ci[2]
))

# Display outputs
h3_table
contingency_table_h3

```

Ordinal Analysis
STEM students reported significantly higher trust levels (Mdn = 3.0) than humanities/social sciences students (Mdn = 3.0), Mann-Whitney U = 2358, *p* = .014. The effect size was small (rank-biserial *r* = 0.20, 95% CI [0.05, 0.35]), indicating a 59.8% probability that a randomly selected STEM student would report higher trust than a humanities/social sciences student (95% CI [52.5%, 67.5%]).

Binary Analysis
STEM students had 2.3× higher odds of exhibiting high trust (≥4 on the scale) than humanities/social sciences students, χ²(1) = 4.79, *p* = .029; 95% CI [1.14, 4.59]. The contingency table revealed:

STEM students: 42.4% high trust (36/85), within-group odds = 0.73

Humanities/Arts students: 24.3% high trust (17/70), within-group odds = 0.32

Justification
The ordinal outcome (trust measured on a 1–5 Likert-type scale) and independent groups (STEM vs. humanities/arts) justified a non-parametric approach. The Wilcoxon rank-sum test (Mann-Whitney U) was selected to compare distributions without assuming normality. The rank-biserial *r* and probability superiority metric were included to quantify practical significance beyond *p*-values.

To augment the ordinal analysis, trust was dichotomized (high = 4–5, low = 1–3) to examine proportional differences via chi-square. The odds ratio (OR = 2.3) indicates STEM students were 2.3 times more likely to report high trust. The 95% confidence interval [1.14, 4.59] excludes 1, supporting a statistically significant association. A chi-square test was chosen over Fisher’s exact test because all expected cell frequencies exceeded 5 (min expected count = 19.3).

Consistency of Evidence
While medians were equal (3.0), the significant U statistic (*p* = .014) and positive effect size (*r* = 0.20) suggest STEM students’ trust distributions skewed higher. This aligns with the binary analysis (higher odds of high trust among STEM students). Narrow CIs for both effect size and odds ratio strengthen evidence for a true effect.

# BONUS: Correlation between AI Use and AI Trust

```{r}

# 1. Create the tab
tab <- table(my_df$AI_Use_Binary, my_df$High_Trust)

# 2. Run Chi-square test
chisq_test <- chisq.test(tab)
chisq_test

# 3. Pretty contingency table
contingency_table <- as.data.frame.matrix(tab) %>%
  tibble::rownames_to_column("AI_Use_Binary") %>%
  mutate(Total = Low + High,
         `% High Trust` = round(High / Total * 100, 1)) %>%
  gt() %>%
  tab_header(
    title = md("**Contingency Table: AI Use Binary vs High Trust**")
  ) %>%
  fmt_number(columns = c(Low, High, Total), decimals = 0) %>%
  cols_label(
    Low = md("**Low Trust**"),
    High = md("**High Trust**"),
    Total = md("**Total**"),
    `% High Trust` = md("**% High Trust**")
  )

# 4. SHOW the table
contingency_table

# Calculate percentages for plotting
plot_data <- as.data.frame(prop.table(table(my_df$AI_Use_Binary, my_df$High_Trust), margin = 1))
colnames(plot_data) <- c("AI_Use", "Trust", "Percentage")

# Create plot
ggplot(plot_data, aes(x = AI_Use, y = Percentage*100, fill = Trust)) +
  geom_col(position = "dodge", width = 0.7) +
  geom_text(aes(label = paste0(round(Percentage*100, 1), "%")), 
            position = position_dodge(width = 0.7), 
            vjust = -0.5, size = 4) +
  scale_fill_manual(values = c("High" = "#4CAF50", "Low" = "#F44336")) +
  labs(title = "Trust in AI by Usage Frequency",
       x = "AI Use Frequency",
       y = "Percentage of Students",
       fill = "Trust Level") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"))

```
There's a statistically significant relationship between AI use and trust levels (χ²(1) = 8.73, p = .003). Students who frequently use AI tools (High AI Use group) are significantly more likely to trust AI outputs compared to infrequent users. While only 27% of low AI users show high trust, this jumps to 55% among high AI users - a doubling of trust levels. This difference is statistically reliable (p < .01).

